### 2014-06-06 paper/paper.tex
adding ttest

The first point to check is if the different weight vectors affect the solutions obtained by MO-MCTS. Table~\ref{tab:weights} shows the results of executing the MO-MCTS controller during $30$ games in each one of the $10$ maps of the MO-PTSP, for every weight vector. This table includes the averages obtained and the p-value for the results of the objective with the highest weight, compared with the result from the default weight vector $W_1 = (0.33,0.33,0.33)$ in the same map. It can be seen that the highest weight in $W$ leads, in most of the cases, to the best solution in that objective in the map.

>>>>

The first point to check is if the different weight vectors affect the solutions obtained by MO-MCTS. Table~\ref{tab:weights} shows the results of executing the MO-MCTS controller during $30$ games in each one of the $10$ maps of the MO-PTSP, for every weight vector. This table includes the averages obtained and the independent t-test p-value for the results of the objective with the highest weight, compared with the result from the default weight vector $W_1 = (0.33,0.33,0.33)$ in the same map. It can be seen that the highest weight in $W$ leads, in most of the cases, to the best solution in that objective in the map.
